### 2022-12-28 quarto/index.qmd
update

<table align="center" width="1000">
<tbody>
<tr>
<td height="200" width="200"><img src="img/aston.jpg" height="150" width="150" border="0" hspace="0" /></td>
<td>
<p align="left"><img src="img/email.png" height="30" width="225"></p>
<p align="left"><span style="font-size: large;">2795 Augustine Dr, Santa Clara, CA 95054</span></p>
<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>
</td>
</tr>
</tbody>
</table>

@@

## <a href="papers.html">All Papers</a>

>>>>

<img src="img/aston.jpg"  border="0" vspace="5" hspace="0" /><br>
<img src="img/email.png" height="30" width="200" vspace="5" ><br>

<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>

@@

## [All Papers](papers.qmd)
